---
title: |
  | Matthias Breuer and David Windisch 
  | (Mis-)Matching and Earnings Properties: Implications of Dynamic Investments
subtitle: "KIT, Ausschuss Unternehmensrechnung VfS" 
author: Joachim Gassen
institute: "HU Berlin"
date: today
date-format: "MMMM D, YYYY"
format: 
  beamer:
    latex_engine: xelatex # pdflatex creates rastered fonts
    slide_level: 3
    
classoption: "aspectratio=169"

header-includes:
- \usepackage{booktabs} 
- \usepackage{tabularx}
- \usepackage{multirow,makecell}
- \usepackage{array}
- \renewcommand\tabularxcolumn[1]{m{#1}}
- \usepackage{makecell}
- \usepackage{colortbl}
- \usepackage{adjustbox}
- \usepackage{tikz}
- \usepackage{siunitx}
- \usepackage{tabu}
- \usetikzlibrary{arrows,arrows.meta,calc,positioning,matrix}
- \input{materials/beamer_theme_trr266_16x9.sty}
---

```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_chunk$set(
  cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE
)

suppressMessages({
  library(tidyverse)
  library(gt)
  library(kableExtra)
  library(modelsummary)
  library(showtext)
	library(tufte)
  devtools::source_url(
    "https://raw.githubusercontent.com/trr266/treat/main/code/R/theme_trr.R"
  )
})

set.seed(42)

panels <- readRDS("../data/generated/panels_600k_100z_600kmax_BW_4000firms_25years.rds") %>%
  group_by(gamma, firm) %>%
  mutate(
    lag_accear = lag(accear),
    price = V
  )
panel <- readRDS("../data/generated/panel_wrds.rds")
# Needs \usepackage{adjustbox} in preamble
fit_gt_table_to_slide <- function(x, scale = 1) {
	if (scale == 1) repstr <- "\\\\resizebox{\\\\columnwidth}{!}{\\\\begin{tabular}"
	else repstr <- paste0("\\\\resizebox{", scale, "\\\\columnwidth}{!}{\\\\begin{tabular}")
  x <- sub("\\\\begin\\{longtable\\}", repstr, x)
  x <- sub("\\\\end\\{longtable\\}", "\\\\end{tabular}}", x)
  x
}

fit_gt_table_to_slide_long <- function(x, scale = 1) {
	if (scale == 1) repstr <- "\\\\resizebox*{!}{\\\\textheight}{\\\\begin{tabular}"
	else repstr <- paste0("\\\\resizebox*{!}{", scale, "\\\\textheight}{\\\\begin{tabular}")
  x <- sub("\\\\begin\\{longtable\\}", repstr, x)
  x <- sub("\\\\end\\{longtable\\}", "\\\\end{tabular}}", x)
  x
}

center_table <- function(x) {
	x[1] <- paste0("\\begin{center}", x[1], "\\end{center}")
	x
}

script_size <- function(x) {
	x[1] <- paste0("\\scriptsize", x[1], "\\normalsize")
	x
}

tiny_size <- function(x) {
	x[1] <- paste0("\\tiny", x[1], "\\normalsize")
	x
}
```

```{r InstallTRRFonts}
trr266_fonts_available <- all(c("Cambria", "Calibri Light") %in% font_families())

if (!trr266_fonts_available) {
  # On Mac with MS Office installation you need to add the Office
  # Fonts to the font path. The following depends on your 
  # installation but _should_ work in most cases
  
  office_font_path <- "/Applications/Microsoft Word.app/Contents/Resources/DFonts"
  if (Sys.info()["sysname"] == "Darwin") {
    if (dir.exists(office_font_path)) font_paths(office_font_path)
    else stop("MS Office font path not found")
  }
  
  rv <- tryCatch({
    font_add(family = "Cambria", regular = "Cambria.ttc")
    font_add(family = "Calibri Light", regular = "calibril.ttf")
  }, error = function(e) {
    message(sprintf("Failed to install TRR 266 fonts: %s", e))
    invisible(font_families())        
  })
  
  trr266_fonts_available <- all(c("Cambria", "Calibri Light") %in% rv)
  if (trr266_fonts_available) message("Successfully installed TRR 266 fonts") 
}
```


## Summary of BW

Using a dynamic investment model as in Breuer and Windisch (JAR, 2019) and including a stylized asset recognition rule the authors show that 

- recognizing investments yields less persistent earnings and lower PE-mutliples
- and that Compustat/CRSP data show a similar pattern when partitioned based on established firm-level measures of unconditional conservatism.

They conclude that earnings persistence and PE-ratios might be doubtful measures of earnings quality:
\vspace{0.5cm}
\begin{quote}
Thus, our findings reveal potentially unexpected consequences of capitalizing versus expensing R\&D- and SG\&A-type expenditures for popular earnings properties, and suggest that caution is warranted when using earnings persistence and price-earnings multiples as indicators of earnings quality.
\end{quote}

## (My) Intuition

1. The only truly exogenous driver of the dynamic model is $e_t \sim \mathcal{N}(0, \sigma)$ of the mean reverting AR(1) profitiability process.
2. This profitability shock drives operating and free cash flow via $\pi_t$.
3. As it propogates into the future ($\rho > 0$), it also triggers current Investment ($I_t$), causing related costs $\psi_t$.
4. The investment and the shocked future level of profitability $z$ affects expected future free cash flows, thereby also affecting value $V_t$.

Recognized earnings reflect the effects of $\pi_t$ and $\psi_z$, making earnings relatively stochastic. Expensed earnings 'mute' these effects by deducting $I_t$ which, as it also is driven by $e_t$, makes earnigs less stochastic (more persistent) 

## Model Data: Persistence ($\gamma = 0.0$, recognized)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
perplot <- function(g) {
  ggplot(panels %>% filter(near(gamma, g)), aes(x = lag_accear, y = accear)) + 
    geom_point(alpha = 0.25) + 
    labs(x = "Earnings (t -1)", y = "Earnings (t)") +
    theme_classic() 
}
perplot(0.0)
```

## Model Data: Persistence ($\gamma = 1.0$, expensed)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
perplot(1.0)
```


## For Comparison: Compustat NA (sample similar to BW(2025))

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
ggplot(panel, aes(x = lag_earnings, y = earnings)) + 
  geom_point(alpha = 0.25) + 
  labs(x = "Earnings (t -1)", y = "Earnings (t)") +
  theme_classic()
```

## For Comparison: Compustat NA (sample similar to BW(2025), winsorized)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
panel_w <- ExPanDaR::treat_outliers(panel)
ggplot(panel_w, aes(x = lag_earnings, y = earnings)) + 
  geom_point(alpha = 0.25) + 
  labs(x = "Earnings (t -1)", y = "Earnings (t)") +
  theme_classic()
```

## Model Data: PE-Multiple ($\gamma = 0.0$, recognized)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
pemultplot <- function(g) {
  ggplot(panels %>% filter(near(gamma, g)), aes(x = accear, y = price)) + 
    geom_point(alpha = 0.25) + 
    labs(x = "Earnings (t)", y = "Value (t)") +
    theme_classic() 
}
pemultplot(0.0)
```

## Model Data: PE-Multiple ($\gamma = 1.0$, expensed)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
pemultplot(1.0)
```


## For Comparison: Compustat NA (sample similar to BW(2025))

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
ggplot(panel, aes(x = earnings_per_share, y = price_per_share)) + 
  geom_point(alpha = 0.25) + 
  labs(x = "EPS (t)", y = "Share Price (t)") +
  theme_classic()
```

## For Comparison: Compustat NA (sample similar to BW(2025), winsorized)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
ggplot(panel_w, aes(x = earnings_per_share, y = price_per_share)) + 
  geom_point(alpha = 0.25) + 
  labs(x = "EPS (t)", y = "Share Price (t)") +
  theme_classic()
```


## Some mostly minor points

- Shouldn't equation (3) read as $z_t = (1 − \rho)\bar{z} + \rho z_{t-1} + \varepsilon_{t}$? (also at bottom of P. 11)?
- Equation (5) seems to lack a closing bracket
- Why does the price equation on P. 14 include the term $(1 - \delta)k_t + I_t$? What is the value of the assets in place besides generating future cash flow that is already included in the sum term (does also not seem to fit your data)?
- Some more detail on the techicalities of the empirical analysis would be nice (outlier treatment, ...)
- How uses PE-multiples as an indicator of earnings quality? ;-)