---
title: |
  | Matthias Breuer and David Windisch 
  | (Mis-)Matching and Earnings Properties: 
  | Implications of Dynamic Investments
subtitle: "KIT, Ausschuss Unternehmensrechnung VfS" 
author: Joachim Gassen
institute: "HU Berlin"
date: today
date-format: "MMMM D, YYYY"
format: 
  beamer:
    latex_engine: xelatex # pdflatex creates rastered fonts
    slide_level: 3
    
classoption: "aspectratio=169"

header-includes:
- \usepackage{booktabs} 
- \usepackage{tabularx}
- \usepackage{multirow,makecell}
- \usepackage{array}
- \renewcommand\tabularxcolumn[1]{m{#1}}
- \usepackage{makecell}
- \usepackage{colortbl}
- \usepackage{adjustbox}
- \usepackage{tikz}
- \usepackage{siunitx}
- \usepackage{tabu}
- \usetikzlibrary{arrows,arrows.meta,calc,positioning,matrix}
- \input{materials/beamer_theme_trr266_16x9.sty}
---

```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_chunk$set(
  cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE
)

suppressMessages({
  library(tidyverse)
  library(showtext)
})

set.seed(42)

source("code/objects_sim_data.R")
source("code/objects_wrds_data.R")
```


## Summary of BW

Using a dynamic investment model as in Breuer and Windisch (JAR, 2019) and including a stylized asset recognition rule the authors show that 

- recognizing investments yields less persistent earnings and lower PE-mutliples,
- and that Compustat/CRSP data show a similar pattern when partitioned based on established firm-level measures of unconditional conservatism.

They conclude that earnings persistence and PE-ratios might be doubtful measures of earnings quality:
\vspace{0.5cm}
\begin{quote}
Thus, our findings reveal potentially unexpected consequences of capitalizing versus expensing R\&D- and SG\&A-type expenditures for popular earnings properties, and suggest that caution is warranted when using earnings persistence and price-earnings multiples as indicators of earnings quality.
\end{quote}


## (My) Intuition

1. The only truly exogenous driver of the dynamic model is $e_t \sim \mathcal{N}(0, \sigma)$ of the mean reverting AR(1) profitability process.
2. This profitability shock drives operating and free cash flow via $\pi_t$.
3. As it propagates into the future ($\rho > 0$), it also triggers investment ($I_t$), causing related costs $\psi_t$.
4. The investment and the shocked future level of profitability $z$ affect expected future free cash flows, thereby also affecting value $V_t$.

Recognized earnings reflect the effects of $\pi_t$ and $\psi_t$, making earnings relatively stochastic. Expensed earnings 'mute' these effects by deducting $I_t$ which, as it also is driven by $e_t$, makes earnings less stochastic (more persistent) 


## Compare to Figures 1 and 2 of BW

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
fig_sim_shock_ear_price +
  theme(text = element_text(size = 18))
```


## Same shock, cash flow effects (free cash flow = earnings expensed)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
fig_sim_shock_cfs +
  theme(text = element_text(size = 18))
```


## Regression coefficients persistence (compare to Table 1, Panel A of BW)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
fig_sim_regcoef_persistence +
  theme(text = element_text(size = 18))
```


## Regression coefficients PE multiples (compare to Table 1, Panel B of BW)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
fig_sim_regcoef_pemultiple +
  theme(text = element_text(size = 18))
```


## Model Data: Persistence ($\gamma = 0.0$, recognized)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
fig_sim_scatter_persistence(0.0) +
  theme(text = element_text(size = 18))
```


## Model Data: Persistence ($\gamma = 1.0$, expensed)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
fig_sim_scatter_persistence(1.0) +
  theme(text = element_text(size = 18))
```


## For Comparison: Compustat NA (sample similar to BW)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
fig_wrds_scatter_persistence(panel_wrds) +
  theme(text = element_text(size = 18))
```


## For Comparison: Compustat NA (sample similar to BW, winsorized)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
fig_wrds_scatter_persistence(panel_wrds_winsorized) +
  theme(text = element_text(size = 18))
```


## Model Data: PE-Multiple ($\gamma = 0.0$, recognized)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
fig_sim_scatter_pemultiple(0.0) +
  theme(text = element_text(size = 18))
```


## Model Data: PE-Multiple ($\gamma = 1.0$, expensed)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
fig_sim_scatter_pemultiple(1.0) +
  theme(text = element_text(size = 18))
```


## For Comparison: Compustat NA (sample similar to BW)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
fig_wrds_scatter_pemultiples(panel_wrds) +
  theme(text = element_text(size = 18))
```


## For Comparison: Compustat NA (sample similar to BW, winsorized)

```{r, fig.width=12, fig.height=5, fig.align="center", fig.showtext = TRUE}
fig_wrds_scatter_pemultiples(panel_wrds_winsorized) +
  theme(text = element_text(size = 18))
```


## Some mostly minor points

- Shouldn't equation (3) read as $z_t = (1 − \rho)\bar{z} + \rho z_{t-1} + \varepsilon_{t}$ (also at bottom of P. 11)?
- Equation (5) seems to lack a closing bracket
- Why does the price equation on P. 14 include the term $(1 - \delta)k_t + I_t$? What is the value of the assets in place besides generating future cash flow that is already included in the sum term (does also not seem to fit your data)?
- Some more detail on the technicalities of the model implementation (e.g., grid, firm initialization) and empirical analysis (e.g., outlier treatment) would be nice
- Who uses PE-multiples as an indicator of earnings quality? ;-)

## All the best for this super nice project!

\begin{center}
\includegraphics[height =0.4\textheight]{"materials/github_repo_qr_code.png"}

\includegraphics[height =0.1\textheight]{"materials/github_logo.png"}
\end{center}